A Survey of Fuzzing and New Technique for Dynamic Analysis

### 2014-03-20 docs/paper/fsuthesis/thesis-template/paper.tex
removed urls, working on abstract

Our technique, dubbed taint-

ADD?
The major impetus for this work is outlined in "A Taint Based Approach for Smart Fuzzing". This paper proposes a fuzzing tool architecture, involving vulnerability detection, followed by taint analysis based upon found vulnerabilities, which drives the generation of intelligent tests. As tests are run they are checked to ensure they provide adequate code coverage, and results are carefully monitored for interesting situations like crashes [A]. The paper also serves as an excellent explanation of the current state and future of fuzzing. In particular, they suggest combining taint analysis with backward slicing. The technique discussed in this paper boils down to an attempt to automatically solve slices like those introduced in [AA], which have been derived from taint analysis as much as possible.

@@

\section{Motivation}
TODO US gov't interest via money, security issues, etc.
Raytheon SI/VUPEN use it.

@@

\section{State of the Field}

TODO current capabilities and shortcomings of fuzzers

@@

\section{Theoretical Difficulties}
TODO programming language theory, i.e. what makes fuzzing hard

@@

	\item [N] Salwan, Jonathan. Shell-storm.org %\url{http://shell-storm.org/blog/Taint-analysis-and-pattern-matching-with-Pin/}

@@

	\item [AE] Mozilla Developer Network. \url{https://developer.mozilla.org/en-US/docs/Web/JavaScript/Reference/Global\_Objects/eval}
	\item [AF] The WebKit Open Source Project. \url{http://www.webkit.org/}

>>>>

Our technique, dynamic slice backsolving, using dynamic taint analysis to watch user input. As user input is introduced, each byte is tracked separately and, when the program transforms or manipulates user input, those transformations are recorded. When branches which depend upon user input are reached, the recorded transformations, if possible, are reversed, backsolving for a new value of a particular byte in user input which will lead execution down a different path in the binary. After execution finishes, input test cases are mutated to reflect this new information, and a new execution test runs.

The inspiration for this technique comes mainly from "A Taint Based Approach for Smart Fuzzing", which proposes a fuzzing tool architecture, involving vulnerability detection, followed by taint analysis based upon found vulnerabilities, which drives the generation of intelligent tests. Dynamic taint analysis tracks which bytes of user input are important in the binary, and these so-called "hot bytes" are made the focus of fuzzing attempts. The paper mentions it is valuable to be able to generate backward slices of program traces. This traces can be run and analyzed by programmers. In the spirit of automation, our work not only generates backward slices based on taint propagation, but also automatically solves these traces to find new byte values. Thus, for a subset of programs, we can determine not only the exact location of user input which determines a branch condition, but also generate precise values for both branch and non-branch cases.

@@

\section{Motivation}

@@

\section{Methodology}

@@

@@

	\item [N] Salwan, Jonathan. Shell-storm.org http://shell-storm.org/blog/Taint-analysis-and-pattern-matching-with-Pin/

@@

	\item [AE] Mozilla Developer Network. https://developer.mozilla.org/en-US/docs/Web/JavaScript/Reference/Global\_Objects/eval
	\item [AF] The WebKit Open Source Project. http://www.webkit.org/
